Plots and tables summarizing results of Poisson simulations

### 2018-12-21 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

Here we create plots and tables to compare SMASH and against other
methods for reconstructing a spatially structured signal from
Poisson-distributed data. Similar to the Gaussian simulations, we
generated data sets using a variety of test functions and intensity
ranges. Specifically, we considered 6 test functions, rescaling the
test function so that the smallest intensity was x and the largest
intensity was y, with (x,y) set to either (1/100, 3), (1/8, 8) or
(1/128, 128). For each combination of test function and intensity
range, we simulated 100 data sets. In the plots and tables below, We
summarize the error (MISE) in the estimates from the 100 data sets in
each setting.

The plots below summarizing the results from the "Bursts" simulations
were included in the manuscript.

@@

Specify the row and column names for the tables:

@@

*Add text here.*

@@

Some of the test functions are defined in `signals.R`:

@@

@@

Combine the results of the simulation experiments into several larger
tables.

```{r get-spikes-results}
mise.bur.table <- cbind(mise.bur.1[methods],
                        mise.bur.8[methods],
                        mise.bur.128[methods])
mise.cb.table  <- cbind(mise.cb.1[methods],
                        mise.cb.8[methods],
                        mise.cb.128[methods])
mise.b.table   <- cbind(mise.b.1[methods],
                        mise.b.8[methods],
                        mise.b.128[methods])
rownames(mise.b.table)   <- table.row.names
rownames(mise.cb.table)  <- table.row.names
rownames(mise.bur.table) <- table.row.names
colnames(mise.b.table)   <- table.col.names
colnames(mise.cb.table)  <- table.col.names
colnames(mise.bur.table) <- table.col.names
```

>>>>

Here we create plots and tables to compare various methods, including
SMASH, for reconstructing a spatially structured signal from
Poisson-distributed data. Similar to the Gaussian simulations, we
generated data sets using a variety of test functions and intensity
ranges. Specifically, we considered 6 test functions, rescaling the
test function so that the smallest intensity was x and the largest
intensity was y, with (x,y) set to either (1/100, 3), (1/8, 8) or
(1/128, 128). For each combination of test function and intensity
range, we simulated 100 data sets. In the plots and tables below, we
summarize the error (MISE) in the estimates computed in the 100 data
sets from each simulation setting.

The plots for the "Bursts" simulations were included in the
manuscript.

@@

These variables specify the row and column names for the tables:

@@

Load the ggplot2 cowplot and xtable packages.

@@

Some of the test functions are defined in `signals.R`, so we load them
here:

@@

Each column shows the results at a different range of intensities.
The individual table entries give the average error (MISE) in the
estimates, in which the average is taken over the 100 data sets
simulated at the given range of intensities.

@@

```{r get-spikes-results, echo=FALSE, eval=TRUE}
mise.bur.table <- cbind(mise.bur.1[methods],
                        mise.bur.8[methods],
                        mise.bur.128[methods])
mise.cb.table  <- cbind(mise.cb.1[methods],
                        mise.cb.8[methods],
                        mise.cb.128[methods])
mise.b.table   <- cbind(mise.b.1[methods],
                        mise.b.8[methods],
                        mise.b.128[methods])
rownames(mise.b.table)   <- table.row.names
rownames(mise.cb.table)  <- table.row.names
rownames(mise.bur.table) <- table.row.names
colnames(mise.b.table)   <- table.col.names
colnames(mise.cb.table)  <- table.col.names
colnames(mise.bur.table) <- table.col.names
```
